### 2010-03-28 docs/architecture/architecture.tex
more additions

The {\tt flame} problem models a planar laminar flame.  Initially cool
fuel and hot ash are put in pressure equilibrium.  Thermal diffusion
transfers heat to the fuel, driving a burning front.

@@

@@

@@

The runtime parameters for the core MAESTRO algorithm are listed
in {\tt MAESTRO/\_parameters}.  That file is parsed at compile-time
by the {\tt MAESTRO/write\_probin.py} script
(along with any other parameter files listed in the {\tt PROBIN\_PARAMETERS}
variable in the {GNUmakefile}, see \S \ref{sec:makefile}).  The script
outputs the {\tt probin.f90} source file.  Each line
in the {\tt \_parameters} file has the form:

{\em parameter} \hskip 10em  {\em data-type} \hskip 10em  {\em value}

\noindent where {\em parameter} is the name of the runtime parameter,
{\em data-type} is one of \{{\tt character}, {\tt real}, {\tt
  integer}, {\tt logical}\}, and the {\em value} specifies the default
value for the runtime parameter.  Comments are indicated by a `{\tt
  \#}' character and a used to produce documentation about the
available runtime parameters.

@@

@@

@@

@@

@@

>>>>

The {\tt flame} problem models a planar laminar flame.  Initially cool
fuel and hot ash are put in pressure equilibrium.  Thermal diffusion
transfers heat to the fuel, driving a burning front.  This problem
does not use the traditional MAESTRO elliptic constraint, but
rather enforces $\nabla \cdot U = S$ as discussed in \cite{SNe}.

@@

\subsection{Defining the Grid and Boundary Conditions}

@@

\item {\tt model\_file }
\item {\tt spherical\_in }
\item {\tt ppm\_type }
\item {\tt max\_levs }
\item {\tt n\_cellx }, {\tt n\_celly }, {\tt n\_cellz }
\item {\tt max\_grid\_size }
\item {\tt prob\_lo\_x }, {\tt prob\_lo\_y }, {\tt prob\_lo\_z }
\item {\tt prob\_hi\_x }, {\tt prob\_hi\_y }, {\tt prob\_hi\_z }
\item {\tt anelastic\_cutoff }
\item {\tt base\_cutoff\_density }
\item {\tt do\_sponge }
\item {\tt grav\_const }
\item {\tt max\_step }
\item {\tt init\_iter }
\item {\tt stop\_time }
\item {\tt plot\_base }
\item {\tt plot\_deltat }
\item {\tt chk\_int }
\item {\tt cflfac }
\item {\tt init\_shrink }
\item {\tt bcx\_lo }, {\tt bcy\_lo }, {\tt bcz\_lo }, 
      {\tt bcx\_hi }, {\tt bcy\_hi }, {\tt bcz\_hi }
\item {\tt pmask\_x }, {\tt pmask\_y }, {\tt pmask\_z }
\item {\tt verbose }
\item {\tt mg\_verbose }
\item {\tt cg\_verbose }
\item {\tt do\_initial\_projection }
\item {\tt init\_divu\_iter }
\item {\tt perturb\_model }

@@

The runtime parameters for the core MAESTRO algorithm are listed
in {\tt MAESTRO/\_parameters}.  That file is parsed at compile-time
by the {\tt MAESTRO/write\_probin.py} script
(along with any other parameter files listed in the {\tt PROBIN\_PARAMETERS}
variable in the {GNUmakefile}, see \S \ref{sec:makefile}).  The script
outputs the {\tt probin.f90} source file.  Each line
in the {\tt \_parameters} file has the form: 
\vskip 3mm
{\em parameter} \hskip 10em  {\em data-type} \hskip 10em  {\em value} 
\vskip 3mm
\noindent where {\em parameter} is the name of the runtime parameter,
{\em data-type} is one of \{{\tt character}, {\tt real}, {\tt
  integer}, {\tt logical}\}, and the {\em value} specifies the default
value for the runtime parameter.  Comments are indicated by a `{\tt
  \#}' character and a used to produce documentation about the
available runtime parameters.

@@

The base state is defined by $\rho_0$, $p_0$, and $w_0$.  There is no
base state composition.  Other arrays are defined as needed, such as
$h_0$, the base state enthalpy.

@@

A number of MAESTRO modules appear frequently throughout the source.
Below, we describe some of the more common functionality of the most
popular modules.

\subsection{\tt average}

@@

eos module variables

eos input types

@@

There are a large number of modules in {\tt boxlib/} that provide
the core functionality for managing grids.  Here we describe
the most popular such modules.

@@

need to describe the routines for adding two multifabs, subtracting,
etc. and norm, etc.
